---
title: "Snack Bar Analysis"
author: "Will Sheehan"
date: "21/12/2021"
output: pdf_document
 
---

```{r}
library(readxl)
library(ggplot2)
library(tidyverse)
SB_data <- read_excel("~/Downloads/SB data.xlsx")
summary(SB_data)
```

```{r}
# Used for cleaning names
install.packages("janitor")
library(janitor) 
# removes spaces and uppercase from col names
SB_data <- SB_data %>%
  clean_names()
SB_data
```

## Visual Representations of Inventory Metrics

```{r SB_data products over time}

ggplot(SB_data, aes(purchase_time, product))+
  geom_point()
```

```{r SB_data product quantity per order}

ggplot(SB_data, aes (product, quantity))+
  geom_point()
```

## These two charts reveal two important peices of information:
* Popcorn and pop are very popular in the summertime
* Freezies and Candy/Chocolate are frequently bought in larger amounts, which should be considered when restocking

##Condiderations:

* This data will be heavily influenced by when the SB is open/ when events are happening
* This data is pulled from a range of time that was drastically skewed due to the pandemic, and not a great representation of overall SB performance